Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-16 longSC.tex
adopt comments from Alice

An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricities $\epsilon_n$~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e. $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
Harmonic $v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
Therefore, the higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}. When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to the ansatz used for the viscous distribution function, and to the correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
Hence, studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.

@@

Existing measurements provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$). The temperature dependence of $\eta/s$ in the QGP was discussed in ~\cite{Csernai:2006zz}. The effects on hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.  A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations has just been initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ alone are unlikely to reveal the details of the temperature dependence of $\eta/s$.
It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurement would provide experimental constraints on theoretical predictions for the individual stages of heavy-ion system evolution independently. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

@@

\section{Data Analysis}
\label{sec:experiment}
Data recorded by ALICE in $\PbPb$ collisions at $\snn=2.76$~TeV during the 2010 heavy-ion run at the
LHC is used for this analysis. Detailed descriptions of the ALICE
detector can be found
in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
Projection Chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudorapidity range $|\eta|<0.8$. Two scintillator
arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias $\PbPb$ events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point along the beam direction are selected. Only charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<p_{\rm T}<5$~GeV/$c$ were taken for the analysis. The charged track quality cuts
described in~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks.
The track reconstruction efficiency and contamination
were estimated from HIJING Monte Carlo
simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
the collision centrality. The reconstruction efficiency increases from
70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
below 1\% for $p_{\rm T}>1$~GeV/$c$.
The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted. This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc. Tracks with kinks (i.e. tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.

@@

The systematic uncertainty due to the track reconstruction was estimated from comparisons between results for the so-called standalone TPC tracks with the 
same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
To correct for non-uniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used. Then each track reconstruction strategy was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
The systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
In addition, we applied the like-sign technique to estimate non-flow contributions to SC$(m,n)$. The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and it is about 7\% for SC(4,3) and 20\% for SC(5,3).

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1. Systematical errors are represented with boxes.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

@@

It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations as well as SC(5,2) increase non-linearly towards peripheral collisions.
In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations and a monotonic increase is observed.
NSC(5,3) shows the strongest normalized correlation among all harmonics while NSC(5,2) shows the weakest centrality dependence.
Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.

\begin{figure*}
	\begin{center}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
        \caption{SC(3,2) and SC(4,2) with low (a) and high (c) minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV. Panels (a) and (b) show the results for the minimum $p_{\rm T}$ range $0.2<p_{\rm T}<0.7$~GeV/$c$ and panels (c) and (d) are for the minimum $p_{\rm T}$ range $0.8<p_{\rm T}<1.5$~GeV/$c$. Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure*}

To study the $p_{\rm T}$ dependence of SC$(m,n)$, we systematically vary the low $p_{\rm T}$ cut-off, instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}a.
The strength of SC$(m,n)$ becomes larger as the minimum $p_{\rm T}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
These $p_{\rm T}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as the centrality or the minimum $p_{\rm T}$ cut increase. 
NSC(3,2) and NSC(4,2) with different minimum cuts are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within the errors for all minimum $p_{\rm T}$ cuts. 
This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the $\left<v_n\right>$ values. 
The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Figs.~\ref{fig:Figure_2}c and \ref{fig:Figure_2}d.
While SC$(m,n)$ shows similar trends as for $p_{\rm T}<0.8$~GeV/$c$, NSC$(m,n)$ tends to decrease with increasing $p_{\rm T}$.
The $p_{\rm T}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T}$ for the $>$~30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ increases. These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

@@

The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics. With well-tuned transport coefficients and decoupling temperature, and given initial condition discussed later, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}. In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions. The model then introduces the string melting procedure to produce initial partons. These partons are then evolved for the short duration using the ZPC parton cascade model. Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution. Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.

@@

\subsection{Low Order Harmonic Correlations}
\label{sec:theory_loworder}
SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}. 
In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
This observation helps us to better understand the fluctuations in initial energy density.
NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values. This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions. The better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.

>>>>

An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricities $\epsilon_n$~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e. $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
Harmonic $v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
Therefore, the higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}. When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitudes of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ are sensitive to the ansatz used for the viscous distribution function, and to the correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
Hence, studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.

@@

Existing measurements provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$). The temperature dependence of $\eta/s$ in the QGP was discussed in ~\cite{Csernai:2006zz}. The effects on hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.  A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations has just been initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ alone is unlikely to reveal the details of the temperature dependence of $\eta/s$.
It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurement would provide experimental constraints on theoretical predictions for the individual stages of the heavy-ion system evolution independently. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

@@

\section{Data Analysis}
\label{sec:experiment}
Data recorded by ALICE in $\PbPb$ collisions at $\snn=2.76$~TeV during the 2010 heavy-ion run at the
LHC is used for this analysis. Detailed descriptions of the ALICE
detector can be found
in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
Projection Chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudorapidity range $|\eta|<0.8$. Two scintillator
arrays (V0) which cover the pseudorapidity  ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias $\PbPb$ events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point along the beam direction are selected. Only charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<p_{\rm T}<5$~GeV/$c$ were included in the analysis. The charged track quality cuts
described in~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks.
The track reconstruction efficiency and contamination
were estimated from HIJING Monte Carlo
simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
the collision centrality. The reconstruction efficiency increases from
70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
below 1\% for $p_{\rm T}>1$~GeV/$c$.
The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted. This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc. Tracks with kinks (i.e. tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.

@@

The systematic uncertainty due to the track reconstruction was estimated from comparisons between results for the so-called standalone TPC tracks with the 
same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
To avoid non-uniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, a hybrid track selection utilizing SPD hits and/or ITS refit tracks combined with TPC information was used.
Then each track reconstruction strategy was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
A systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
In addition, we applied the like-sign technique to estimate non-flow contributions to SC$(m,n)$. The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and is about 7\% for SC(4,3) and 20\% for SC(5,3).

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1. Systematic errors are represented with boxes.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

@@

It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations as well as SC(5,2) increase non-linearly towards peripheral collisions.
In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations.
NSC(5,3) shows the strongest normalized correlation among all harmonics while NSC(5,2) shows the weakest centrality dependence.
Both NSC(3,2) and NSC(4,3) are getting more anticorrelated toward peripheral collisions with the similar magnitude.

\begin{figure*}
	\begin{center}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
        \caption{SC(3,2) and SC(4,2) with low (a) and high (c) minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV. Panels (a) and (b) show the results for the minimum $p_{\rm T}$ range $0.2<p_{\rm T, min}<0.7$~GeV/$c$ and panels (c) and (d) are for the minimum $p_{\rm T}$ range $0.8<p_{\rm T, min}<1.5$~GeV/$c$. Note that NSC data points from each $p_{\rm T, min}$ in a centrality percentile bin are shifted for visibility.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure*}

To study the $p_{\rm T}$ dependence of SC$(m,n)$, we systematically vary the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T, min}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}a.
The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
These $p_{\rm T, min}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as the centrality or $p_{\rm T, min}$ increase. 
NSC(3,2) and NSC(4,2) with different minimum cuts are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within the errors for all $p_{\rm T, min}$ cuts. 
This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the $\left<v_n\right>$ values. 
The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Figs.~\ref{fig:Figure_2}c and \ref{fig:Figure_2}d.
While SC$(m,n)$ shows similar trends as for $p_{\rm T, min}<0.8$~GeV/$c$, NSC$(4,2)$ tends to decrease with increasing $p_{\rm T, min}$.
The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ increases. These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

@@

The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics. With well-tuned transport coefficients and decoupling temperature, and given initial conditions discussed later, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}. In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions. The model then introduces the string melting procedure to produce initial partons. These partons are then evolved for the short duration using the ZPC parton cascade model. Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution. Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.

@@

\subsection{Low Order Harmonic Correlations}
\label{sec:theory_loworder}
SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}. 
In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
This observation helps us to better understand the fluctuations in initial energy density.
NSC(4,2) shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values. This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions. Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.
